HTW

### 2023-10-12 Manuscript/manuscript.qmd
re-render manuscripts

---
title: "HTW"
short-title: "Variability and Extrapolation"
date: last-modified
author:
- name: Thomas Gorman
  affiliation: Indiana University
  url: www.tegorman13.github.io
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Rob Goldstone
  affiliation: Indiana University
  url: www.pc.cogs.indiana.edu 
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
abstract: |
  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations. 
keywords:
  - Learning Generalization
  - Function Learning
  - Visuomotor learning
  - Training Variability
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/htw>"
bibliography: ../Assets/Bib/HTW.bib
link-citations: true
keep-md: true
---

>>>>

---
title: "HTW"
short-title: "Variability and Extrapolation"
date: 10-11-2023
author:
- name: Thomas Gorman
  affiliation: Indiana University
  url: www.tegorman13.github.io
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Rob Goldstone
  affiliation: Indiana University
  url: www.pc.cogs.indiana.edu 
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
abstract: |
  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations. 
keywords:
  - Learning Generalization
  - Function Learning
  - Visuomotor learning
  - Training Variability
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/htw>"
bibliography: ../Assets/Bib/HTW.bib
link-citations: true
keep-md: true
---
